\speculake: Hiding Malware in Speculative Execution

### 2018-05-08 paper/implementation.tex
add instructions per second

\TODO{Ian: how many seconds did it take to complete?}
We implemented the 5 state Busy Beaver configuration which requires over 47
million steps to complete. We were able to verify that the speculative world
could correctly compute 20 thousand steps with no errors.

>>>>

We implemented the 5 state Busy Beaver configuration which requires over 47
million steps to complete. We were able to verify that the speculative world
could correctly compute 20 thousand steps with no errors at a rate of 324 instructions per second.
